\Large{Adversarial Training against Systematic Uncertainty}

### 2016-09-28 tex/paper.tex
save

>>>>

\glnote{Discuss practical considerations regarding the stability of training. A
better alternative seems to update $r$ until it is good
enough, then update $f$, and update $r$ again as soon as it becomes too bad.
This is important e.g. for MDN to prevent weights to explode if the network is
trained too much, and in which case gradients become useless.} \glnote{Warn against
setting $\lambda$ too high, since it could simply force $f$ to produce unlikely
and very bad decisions.}
